A Topography of Climate Change Research

### 2018-09-04 pres/2018_02_pres.tex

@@

\begin{frame}
	The documents that underpin this growth
\end{frame}

\begin{frame}{Results - Development}
\only<1->{
	\begin{figure}
		\includegraphics[width=0.6\linewidth]{../plots/development/ar5_growth}	
	\end{figure}
}
\only<1->{
	\centering
	\textbf{Fast growing topics in AR5 were on urban systems, negative emissions, buildings, consumption, biodiversity and risks}
}
\end{frame}

\begin{frame}{Results - Development}
\only<1->{
\begin{figure}
	\includegraphics[width=0.8\linewidth]{../plots/development/ar6_growth}	
\end{figure}
}
\only<1->{
	\centering
	\textbf{Negative emissions topics continue to grow,}
}
\end{frame}

@@

%\begin{frame}{Preliminary results - structure - WGI}
%
%\begin{columns}
%	\begin{column}{0.65\linewidth}
%		\begin{center}
%			\vspace*{-0.1\linewidth}
%%			\includegraphics[width=1.1\linewidth]{../plots/network_wg_372_1.PNG}
%		\end{center}
%	\end{column}
%	\begin{column}{0.35\linewidth}
%%		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key.PNG}
%		\begin{center}
%			\begin{itemize}
%				\item The largest topic in WGI is on models.
%			\end{itemize}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}
%
%\begin{frame}{Preliminary results - structure - WGII}
%
%\begin{columns}
%	\begin{column}{0.65\linewidth}
%		\begin{center}
%			\vspace*{-0.1\linewidth}
%			\includegraphics[width=1.1\linewidth]{../plots/network_wg_372_2}
%		\end{center}
%	\end{column}
%	\begin{column}{0.35\linewidth}
%		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key}
%		\begin{center}
%			\begin{itemize}
%				\item The largest primarily WGII topic is on climate change impacts
%			\end{itemize}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}
%
%\begin{frame}{Preliminary results - structure - WGIII}
%
%\begin{columns}
%	\begin{column}{0.65\linewidth}
%		\begin{center}
%			\vspace*{-0.1\linewidth}
%			\includegraphics[width=1.1\linewidth]{../plots/network_wg_372_3}
%		\end{center}
%	\end{column}
%	\begin{column}{0.35\linewidth}
%		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key}
%		\begin{center}
%			\begin{itemize}
%				\item The largest WGIII topic is on emissions reductions.
%			\end{itemize}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}
%
%\begin{frame}{Preliminary results - structure - other clusters}
%
%\begin{columns}
%	\begin{column}{0.65\linewidth}
%		\begin{center}
%			\vspace*{-0.1\linewidth}
%			\hspace*{-0.1\linewidth}
%			\includegraphics[width=1.25\linewidth]{../plots/network_wg_372_4}
%		\end{center}
%	\end{column}
%	\begin{column}{0.35\linewidth}
%		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key}
%		\begin{center}
%			\begin{itemize}
%				\item A fourth cluster of mostly WGII references contains topics on ecosystems, species and habitats
%			\end{itemize}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}

%\begin{frame}{Preliminary results - structure - Sustainability}
%
%
%
%\begin{columns}
%	\begin{column}{0.6\linewidth}
%		\begin{center}			
%			\includegraphics[width=\linewidth]{../plots/sustainability}
%		\end{center}
%	\end{column}
%	\begin{column}{0.4\linewidth}
%		\begin{center}
%			\begin{itemize}
%				\item In later assessment periods, a large meta-topic on research priorities and sustainability emerges
%			\end{itemize}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}
%
%\begin{frame}{Preliminary results - structure - Sustainability}
%
%
%
%\begin{columns}
%	\begin{column}{0.6\linewidth}
%		\begin{center}			
%			\includegraphics[width=\linewidth]{../plots/health_sustain_386}
%		\end{center}
%	\end{column}
%	\begin{column}{0.4\linewidth}
%		\begin{center}
%			\begin{itemize}
%				\item The flatness of its distribution across documents indicates a topic that occurs
%			\end{itemize}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}
%
%%% Sus table
%
%\begin{frame}{Preliminary results - structure - Sustainability}
%\begin{table}
%	\footnotesize
%	\renewcommand{\arraystretch}{2}
%\begin{tabular}{p{0.3\linewidth}p{0.3\linewidth}p{0.3\linewidth}}
%	\toprule 
%	{polici, govern, tax} & {adapt, vulner, strategi}  & {urban, citi, area} \\ 
%	\midrule 
%	How Research-Prioritization Exercises Affect Conservation Policy & Methodological choices in solution-oriented adaptation research: a diagnostic framework & A review of urban ecosystem services: six key challenges for future research  \\ 
%	Role of hydrology and economics in water management policy under increasing uncertainty & When not every response to climate change is a good one: Identifying principles for sustainable adaptation & Lines of Tradition and Recent Approaches to Urban Ecology, Focussing on Germany and the USA \\ 
%	Informing food policy: balancing the evidence & Informed adaptation: Ethical considerations for adaptation researchers and decision-makers & Advancing understanding of the complex nature of urban systems \\ 
%	The identification of priority policy options for UK nature conservation & Future oriented conservation: knowledge governance, uncertainty and learning & Sustainable urban landscapes: South African perspectives on transdisciplinary possibilities \\ 
%	Environmental education policy research challenges and ways research might cope with them & Towards an integrated agenda for adaptation research: theory, practice and policy & A conceptual framework for addressing complexity and unfolding transition dynamics when developing sustainable adaptation strategies in urban water management \\
%	\bottomrule
%\end{tabular} 
%
%\end{table}
%
%\end{frame}

%\begin{frame}{Preliminary results - growth}
%
%\begin{columns}
%	\begin{column}{0.6\linewidth}
%		\begin{center}
%			\includegraphics[width=\linewidth]{../plots/top_20_386}
%		\end{center}
%	\end{column}
%	\begin{column}{0.4\linewidth}
%		\begin{center}
%			\begin{itemize}
%				\item Negative emissions related topics have shown strong growth since the end of AR5
%				\item As have topics on cities and extreme weather events
%			\end{itemize}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}

%\begin{frame}{Preliminary results - growth - biochar}
%
%
%		\begin{center}
%			\includegraphics[width=\linewidth]{../plots/biochar_growth.png}
%
%		\medskip
%
%			\begin{itemize}
%				\item Biochar has emerged as an entirely new topic in the last 10 years
%			\end{itemize}
%		\end{center}
%
%\end{frame}

%\begin{frame}{Preliminary results - gaps in coverage}
%
%How can we get a sense of which topics are better covered in IPCC reports?
%
%\begin{itemize}
%	\item Each document \(d\) either matches or does not match an IPCC reference
%	\item For each topic \(h\), we can sum the scores for each category of document
%	\item The ``IPCC proportion'' of each topic is the proportion of the sum of the document score accounted for by documents which match IPCC references.
%\end{itemize}
%
%\end{frame}

@@

How can we get a sense of which topics are better covered in IPCC reports?

@@

We get a measure of proportionality between two distributions by dividing the each topics share in the IPCC sample by its share in the whole corpus

@@

	\includegraphics[width=0.8\linewidth]{../plots/ipcc_coverage_by_wg_654.png}

@@

Outlines for the sixth assessment report have already been published.

The words in each chapter were matched to the Topic-Term matrix generated by the model to calculate a [simplified] topic score for each chapter.

These scores were summed and were compared to the corpus in general in the same way as with past reports

@@

%\begin{frame}{Conclusions}
%
%
%\begin{itemize}
%	\item Endogenously discovered topics make substantive sense of an unmanageable dataset of climate-relevant literature
%	\item Topic modelling discovers over-arching topics such as that on sustainability and research priorities, as well as individual, fast growing topics such as biochar or CCS
%	\item Matching documents to IPCC references, we can describe topics that belong to or bridge IPCC working groups
%	\item Quantitative evidence is found to support policy makers' dissatisfaction with a lack of `solution orientation' in IPCC reports \citep{Kowarsch2017} 
%	\item By uncovering the structure at scale of a large collection of documents, and by enabling the discovery of documents relevant to specific topics or combinations of topics, this approach can provide for more comprehensive and salient scientific assessments.
%\end{itemize}
%
%\end{frame}

@@

\begin{frame}{Frame Title}
	\small
	\bibliography{../Mendeley.bib}
\end{frame}

>>>>

\begin{frame}{Results - Inter-working Group topics - WG 1 and 2}

@@

\begin{frame}
	\begin{figure}
		\includegraphics[width=\linewidth]{../plots/sus_overview}
	\end{figure}
\end{frame}

\begin{frame}{Results - Development}
\only<1->{
	\begin{figure}
		\includegraphics[width=0.8\linewidth]{../plots/ar5_growth_662}	
	\end{figure}
}
\only<1->{
	\centering
	\textbf{Fast growing topics in AR5 were on urban systems, negative emissions, buildings, consumption, biodiversity and risks}
}
\end{frame}

\begin{frame}{Results - Development}
\only<1->{
\begin{figure}
	\includegraphics[width=0.8\linewidth]{../plots/ar6_growth_662}	
\end{figure}
}
\only<1->{
	\centering
	\textbf{Negative emissions topics continue to grow,}
}
\end{frame}

@@

@@

\begin{itemize}
	\item<1-> How can we get a sense of which topics are better covered in IPCC reports?
	\item<2-> We get a measure of proportionality between two distributions by dividing the each topics share in the IPCC sample by its share in the whole corpus
	\item<3-> This and other measures come from literature on the proportionality of electoral systems \citep[e.g][]{Karpov2008}
\end{itemize}

@@

@@

\begin{columns}
	\begin{column}{0.7\linewidth}
				\includegraphics[width=\linewidth]{../plots/ipcc_coverage_by_wg_654.png}
	\end{column}
	\begin{column}{0.3\linewidth}
		\begin{itemize}
			\item On average, topics that are primarily referenced by working group I report have a higher proportion of constituent documents matching IPCC references
		\end{itemize}
	\end{column}
\end{columns}

@@

\begin{itemize}
	\item<1-> Outlines for the sixth assessment report have already been published
	\item<2-> The words in each chapter were matched to the Topic-Term matrix generated by the model to calculate a simplified topic score for each chapter
	\item<3-> These scores were summed and were compared to the corpus in general in the same way as with past reports
\end{itemize}

@@

\begin{frame}{Conclusions}

\begin{itemize}
	\item<1-> Endogenously discovered topics map and make substantive sense of an unmanageable dataset of climate-relevant literature
	\item<2-> Topic modelling discovers over-arching topics such as that on sustainability and research priorities, as well as specific, fast growing topics such those on negative emissions
	\item<3-> Some quantitative evidence is found to support policy makers' dissatisfaction with a lack of `solution orientation' in IPCC reports \citep{Kowarsch2017} 
\end{itemize}

\begin{frame}{Discussion}

\begin{itemize}
	\item<1-> A perfectly representative relationship between the literature and IPCC reports is not necessarily desirable
	\item<2-> The IPCC are best placed to decide which aspects of the literature to emphasise
	\item<3-> A topography of the literature helps to address issues of emphasis from a point of understanding, and to make decisions clear and transparent
	\item<4-> More generally, maps like this present exciting opportunities to aid the process of literature selection, and to understand the science policy process
\end{itemize}

@@

\begin{frame}{A Topography of Climate Change Research}
\begin{columns}
	\begin{column}{0.5\linewidth}
		\begin{center}
			\begin{figure}
				\includegraphics[width=1\linewidth]{../plots/Hondius_Portrait_of_map-makers}
				\caption{Portrait of map-makers, Gerard Mercator and Jodocus Hondius (Jodocus Hondius) source: \url{https://commons.wikimedia.org/wiki/File:Hondius_Portrait_of_map-makers.jpg}}
			\end{figure}
		\end{center}
	\end{column}
	\begin{column}{0.5\linewidth}
		\begin{center}
\includegraphics[width=\linewidth]{../plots/pca_map_portrait}
		\end{center}
	\end{column}
\end{columns}
\end{frame}

\begin{frame}{Bibliography}
	\small
	\bibliography{../Mendeley.bib}
\end{frame}
